Concurrent Programming in Harmony

### 2022-01-10 book/paper.tex
Trying to add a list of figures to book
Added list of figures to the book

\tableofcontents

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.9\textwidth]{figures/Up1.png}
\end{center}
\caption{The
\harmonyref{Up.html}{HTML output of running Harmony on \autoref{fig:inc}}.
There are four sections.
The top shows the turns to the problematic state.
Each turn shows a thread identifier, the method the thread is executing,
a ``timeline'' containing a block for each instruction executed, the
program counter of the thread, the values of the shared variables
at those turns, and any values the program may have printed.
The middle section shows the line of code that is being executed.
The bottom left shows the bytecode of the program.
The bottom right shows the state of each thread.
Each row in the stack trace of a thread shows
the method that is being evaluated and
the values of its method variables.}
\label{fig:inchtml1}
\end{figure}

@@

>>>>

\tableofcontents
\listoffigures

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.9\textwidth]{figures/Up1.png}
\end{center}
\caption{The
\harmonyref{Up.html}{HTML output of running Harmony on \autoref{fig:inc}}.
% There are four sections.
% The top shows the turns to the problematic state.
% Each turn shows a thread identifier, the method the thread is executing,
% a ``timeline'' containing a block for each instruction executed, the
% program counter of the thread, the values of the shared variables
% at those turns, and any values the program may have printed.
% The middle section shows the line of code that is being executed.
% The bottom left shows the bytecode of the program.
% The bottom right shows the state of each thread.
% Each row in the stack trace of a thread shows
% the method that is being evaluated and
% the values of its method variables.
}
\label{fig:inchtml1}
\end{figure}

@@

\addtocontents{toc}{\protect\setcounter{tocdepth}{2}}
